% Created 2023-01-27 Fri 19:48
\documentclass[9pt, b5paper]{article}
\usepackage{xeCJK}
\usepackage{minted}
\usepackage[T1]{fontenc}
\usepackage[scaled]{beraserif}
\usepackage[scaled]{berasans}
\usepackage[scaled]{beramono}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{float}
\usepackage{textcomp}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{latexsym}
\usepackage{natbib}
\usepackage{geometry}
\geometry{left=1.2cm,right=1.2cm,top=1.5cm,bottom=1.2cm}
\newminted{common-lisp}{fontsize=\footnotesize} 
\usepackage[xetex,colorlinks=true,CJKbookmarks=true,linkcolor=blue,urlcolor=blue,menucolor=blue]{hyperref}
\author{deepwaterooo}
\date{\today}
\title{unity游戏热更新服务端服务器}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 27.2 (Org mode 8.2.7c)}}
\begin{document}

\maketitle
\tableofcontents


\section{An Android Todo-list sample application to play with Realm.}
\label{sec-1}

\subsection{Features}
\label{sec-1-1}
\subsubsection{Basic Features}
\label{sec-1-1-1}
\begin{itemize}
\item Home List: List of lists.
\begin{itemize}
\item Query all lists.
\item Add a new list.
\item Delete a list.
\item Edit a list.
\item Click to show list detail.
\item FAB to add a task and choose a target list.
\end{itemize}
\item List Detail: List of tasks.
\begin{itemize}
\item Query all tasks in this list.
\item Add a new task.
\item Delete a task.
\item Mark a task as done.
\item Click to show task detail.
\item Show all completed tasks.
\item Mark a completed task as to-do.
\end{itemize}
\item Task Detail.
\begin{itemize}
\item Edit a task's title.
\item Edit a task's note.
\end{itemize}
\end{itemize}

\subsubsection{Features backlog}
\label{sec-1-1-2}
\begin{itemize}
\item $\square$ Add due date to task.
\item $\square$ About screen.
\item Confirm before deleting.
\item $\square$ Task priority, mark a task as important, urgent or current doing.
\item $\square$ Drag to change the item order in list.
\item $\square$ Settings screen:
\begin{itemize}
\item $\square$ Change the color theme of the app.
\item $\square$ Send feedback.
\end{itemize}
\end{itemize}

\subsection{References}
\label{sec-1-2}
\begin{itemize}
\item\relax [realm-java](\url{https://github.com/realm/realm-java})
\item\relax [Realm Doc](\url{https://realm.io/docs/java/latest/})
\item In Progress, will make it work in the evening \url{https://www.cnblogs.com/mengdd/p/android-realm-database-guides.html}
\item easily migration into AndroidX. will study source code to digest necessary concepts and the project better. Love my dear cousin!
\end{itemize}
% Emacs 27.2 (Org mode 8.2.7c)
\end{document}